---
title: "Cytomegalovirus Data Analysis"
format: html
editor: visual
---

## EPI 590R Final Project, Danning Tian

1.  Read in raw data

```{r}
#| message: false
#| echo: true

library(tidyverse)
library(gtsummary)

cyto <- get(load(here::here("data","cytomegalovirus.rda")))
cyto$sex_cat <- factor(cyto$sex, 
                       levels = c(0, 1),
                       labels = c("Female", "Male"))
```

This data set contains `r nrow(cyto)` consecutive patients who underwent T-cell replete, matched sibling donor reduced-intensity conditioning allogeneic hematopoietic stem cell transplant. `r nrow(cyto$sex==0)` are females. The patients' diagnosis are carefully noted, including `r unique(cyto$diagnosis)[1:2]` and so on.

2.  Create a {gtsummary} table of descriptive statistics about your data

```{r}
#| label: tbl-initial
#| tbl-cap: "Arranged by sex"
cyto1 <- tbl_summary(cyto, by = sex_cat,
						include = c(diagnosis.type, TNC.dose, CD34.dose,
												aKIRs,TBI.dose, cgvhd, time.to.cgvhd),
						label = list(
							diagnosis.type ~ "Diagnosis type",
							TNC.dose ~ "TNC",
							CD34.dose ~ "CD34",
							aKIRs ~ "Activating killer immunoglobulin-like receptors",
							cgvhd ~ "Precense of cytomegalovirus reactivation",
							time.to.cgvhd ~ "Time to cytomegalovirus reactivation"
						))
as_gt(cyto1)
```

3.  Fit a regression and present well-formatted results from the regression

```{r}
tbl_uvregression(
	cyto,
	y = cgvhd,
	include = c(
		sex_cat,diagnosis.type, TNC.dose, CD34.dose,aKIRs,TBI.dose
	),
	method = glm,
	method.args = list(family = binomial()),
	exponentiate = TRUE
)
```

4.  Create a figure

```{r}
#| label: fig-hist
#| fig-cap: "Spread of aKIRs"
hist(cyto$aKIRs)
```


5.  Write and use a function that does something with the data

```{r}
#Function that calculate the identify whether a patient's time to transplant is below or above the average time to transplant.
average_idf <- function(x, na.rm = TRUE){
	meantime <- mean(cyto$time.to.transplant, na.rm = TRUE)
	if (na.rm) {
		x <- na.omit(x)
	}
	idf <- ifelse(x >= meantime,
				 "More than or Equal to the meantime",
				 "Less than the meantime")
	return(idf)
}

average_idf(cyto$time.to.transplant)
```
